High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2020-10-17 Draft_V4046Sgr_mnras.tex
SC edits will it finally work?

Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig. \ref{fig:two}). Since this faint central emission is offset from the star, at the origin of coordinates in the figure, it is probably due to large dust grains. This dust structure is at a distance of only $\sim0\farcs02$ from the binary system.

@@

\citet{dOrazi} reported a binary phase in the scattered-light observation around 106\,$\degr$, setting $\phi=$0 from the North and increasing clockwise. Using this measurement, the binary phase was calculated at the time of the ALMA observation at $\phi=$13\,$\degr$. There is no clear signal of any shadow similar to the ones present in the DPI image, this could be explained by inefficient disk cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.

@@

To search for a possible model that could explain the available data, we perform radiative transfer modelling with \textsc{radmc3d} \citep{Dullemond_2012}. Here we describe a 3D modelling framework for constructing disc structures given some parameters to characterise it. The model environment is similar to the one used by \citet{2018MNRAS.477.5104C} for DoAr 44.

For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of log$\,\dot{\mathrm{M}} = -$9.3\,Myr$^{-1}$ for both cases \citep{10.1111/j.1365-2966.2011.19366.x}. The stars were placed with a separation of 0.041\,au and oriented with a 30\,$\degr$ rotation, relative to the semi-major axis of the disk, to match the shadows reported by \citet{dOrazi}.

Recreating the complex radial and vertical structure of the V4046\,Sgr disc is not an easy task. We choose to build the model by thinking the components of the disc separately and then unite them as a whole. Given the observations that we are using, we consider that a correct approach for this disc is using two different dust populations: larger grains that are vertically settled and dominates the disc mass and a less-abundant population of smaller grains that are distributed to larger heights from the mid-plane. As the gas and the small-dust population are coupled, it is important to consider the gas in the modelling process, but no line emission prediction is made.

Assuming a three dimensional model in a spherical reference frame with coordinates ($r$, $\theta$, $z$), the gas density ($\rho_{\mathrm{gas}}$) distribution follows
\begin{equation}
  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma(r) \,\delta(r)}{\sqrt{2\pi} \,r H(r)}  \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{r H(r)}\right)^2\right].
\end{equation}
Where $\delta(r)$ is a parameter that indicates the density drops in the gaps and cavities, $H(r)$ is the scale height profile and $\Sigma(r)$ been the surface density profile. $\Sigma(r)$ is defined by
\begin{equation}
  \Sigma(r) = \Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
\end{equation}
where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient. A fixed $\gamma$ = 1 is used as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.

We define the parametric scale height profiles for the gas and for each dust population as
\begin{equation}
    \label{scale}
  H(r)=\chi \, H_{o}(r) \, [r/r_{o}(r)]^{\psi(r)},
\end{equation}
where $H_o$ is the scale height at r = $r_o$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling. For the gas and the micron-sized grains $\chi$ = 1 and for the millimetre-size dust population, as \citet{Rosenfeld_2013}, we assign a fixed $\chi$ = 1/2 for simplicity.

The small-dust density distribution follows the same behaviour as the gas but with different scaling factors: the dust-to-gas ratio ($\zeta$ = 0.047 as \citet{Rosenfeld_2013}), the mass fraction between small and large dust particles ($f_{\mathrm{mass}}$) and another $\delta_{\mathrm{sd}}(r)$ factor for fine tuning that depends on the radius. So it is
\begin{equation}
\rho_{\mathrm{small-dust}}(r,z)=\rho_{\mathrm{gas}}(r,z)\, f_{\mathrm{mass}} \, \delta_{\mathrm{sd}}(r) \: \zeta .
\end{equation}

Since the large-dust grains are less coupled to the gas, their distribution has some important differences. A large inner cavity and another scaling factor (or filter) is needed to generate the larger gap between the rings. For the inner ring, the same profile as the gas is used, but with different values for $R_c$ and $\Sigma_c$. The greatest difference is in the outer ring, where we used a sum of an exponential correction with a Gaussian function and, between 32 and 34.5\,au, in an effort to recreate the break seen in the profile, we chose a different value for $\gamma$ = -8. So, for the large dust grains, the surface density is

\begin{multline}
  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma}  \\ \, \left\{ \mathrm{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] +  \mathrm{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2}\right]\right\}.
\end{multline}

Also for both dust populations, the inner part of the outer ring follows a different behaviour. The surface density profile is multiplied by an additional factor
\begin{equation}
    \epsilon(r) = \delta +  (1 - \delta) \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3,
\end{equation}
where $\delta=10^{-4}$ and $R_\mathrm{in}$ and $R_\mathrm{peak}$ would depend on the dust population, marking the beginning and the maximum density peak of the outer ring. This parameter allow us to model a smoother inner wall of the outer ring.

The two different populations of dust grains vary in size, the small grains range from 0.4 to 1.5\,$\micron$ and the large dust grains range from 0.4\,$\micron$ to 10\,mm. For absorption and opacities of dust populations we assume a typical ISM mineralogical composition, containing 70\% silicate and 30\% graphite.

In an effort to obtain a similar asymmetry as the one observed in the DPI image, the simulated image at 1.65\,$\micron$ had to be taken using a special grain size distribution. Our approach was using a Gaussian size distribution centred at 0.4\,$\micron$, smearing out the grain size by 30\% in both directions and using 20 grain size samples in that range.

\begin{figure}
	\includegraphics[width=\columnwidth]{allprofiles.png}
    \caption{Top panel shows the surface density profiles for the gas, the large and small grain populations. Bottom panel shows the scale height $h(r)$ as a function of polar radius. The dashed lines crossing both panels are the radii that confine the structures.}
    \label{fig:profiles}
\end{figure}

Through trial and error, we found a set of values for the parameters that define a model that correctly fits the available data. The final structure of the parametric model goes as Fig. \ref{fig:profiles} shows. The inner radius of the model grid was set to 0.1\,au and an otter radius of 115\,au, large enough for the dust disc to become undetectable.

The dust begins at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}. For the small dust grains, we propose a three ringed structure. The innermost ring of the model is located from 5 to 8\,au, this ring (Ring6) is not present in the observations but was added for having a better SED fit. Then follows the two observed rings: the first goes from 12 to 19.5\,au (Ring13) and, with a 1\,au-wide gap between them, the outer ring (Ring24) goes from 20.5\,au and has its maximum density peak at 25\,au. The small-dust density then then fades as the radius increases.

On the other hand, in order to reproduce the two ringed observed morphology of the millimetre continuum emission we required a model that has its large-dust grain population distributed with a wide central cavity (r = 12.3\,au), a narrow 2.6\,au-wide inner ring (Ring13) followed by a gap of 8.2\,au that separates both rings and then an outer ring (Ring24) that goes from 23\,au and has it density peak at 27.3\,au. This last ring has a break between 32 and 34.5\,au and then reaches out to 57\,au.

For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one. For that matter, the model uses two different flaring index $\psi$. The separation between the two values was set at $r$ = 19\,au with values of 0.2 for the Ring6 and Ring13 and 0.5 for Ring24. Also, the scale height is calculated using $H_o$ = 0.045 and $r_0$ = 19.5\,au.

@@

The simulated 1.3\,mm continuum image displays some clear similarities with the ALMA observation. The model reproduced the two visible rings: the faint inner Ring13 and the outer brighter Ring24. As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig. \ref{fig:radprofiles}), we can assume that the model provides a reliable approximation of the disc structure, including, particularly for our interest, the dimensions of the previously unseen 1.3\,mm thin inner Ring13. Accordingly, taking the parametric model values for Ring13 we have that it is located at 13.6\,au, has an estimated width of 2.6\,au, an estimated scale height ranging from 0.25 to 0.32\,au and a dust mass of about 3\,M$_{\earth}$. For Ring24, we have that it has an intensity peak at $\sim$30\,au, a break present at $\sim$35\,au and a mass of $\sim$43\,M$_{\earth}$.

As \citet{2018ApJ...869L..46D} explains, the stability of a narrow dust ring can be analysed comparing its height to its radial extent. For a ring to be stable and long-lived its horizontal dimension can not be less than its vertical height. Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of Ring13 (4.17\,au, see Section \ref{sec:Observations}), we have that its width is $\sim$15 times its scale height, meaning that it is stable.

Fig. \ref{fig:SED} shows the SED constructed from the model compared to the photometry data available in the literature in \citet{Jensen_97} and online in \textsc{vizier} and \textsc{diana}, and also using spectrometry data from an archival \textit{Spitzer} IRS spectrum. From the similarity between the data and the resulting SED of the model we confirm that there has to be a small-grain population close to the stars down to 0.3\,au. The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit, this proposed ring (Ring6) has not been observed. The unexpected central emission in the 1.3\,mm continuum image could be part of this inner ring and, as it is asymmetric, the Ring6 could be lopsided.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{SED_.png}
    \caption{The SED (black points and solid red curve) compared with the model (blue). The black points represent the measured photometry and the red line shows an archival \textit{Spitzer} IRS spectrum. The dashed silver curve shows the emission of the stellar photosphere model.}
    \label{fig:SED}
\end{figure}

@@

New ALMA 1.3\,mm continuum imaging of the circumbinary disc around V4046\,Sgr reveals new information about its substructure. Using a radiative transfer model and decompositions in polar coordinates of the computed {\tt uvmem} model image, we measured and analysed the previously unseen thin inner ring and studied the small-dust population distribution.

The key conclusions of our analysis are as follows.
\begin{enumerate}

  \item We report a narrow inner ring for the 1.3\,mm continuum located at 13.46$\pm$0.43\,au from the stars and has an estimated width of 4.17$\pm$0.94\,au. The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes a considerable mass of millimetre-sized grains of around 3\,M$_{\earth}$. Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is $\sim$15 times its estimated height, making it a stable ring.

  \item The 1.3\,mm outer ring, that starts at $\sim$23\,au and has its peak intensity at $\sim$32\,au, presents a visible break in the surface brightness at $\sim$35\,au.

  \item We interpret the asymmetry observed with SPHERE-IRDIS at 1.65\,$\micron$ as due to strong forward-scattering, which implies that the dust population is depleted of grains smaller than $\sim$0.4\,$\micron$.

  \item As our parametric model accounts for the SED of the system, the disc requires the existence of a sub-micron dust population close (<5\,au) to the stars. We also predict the existence of another thin ring at $\sim$6\,au, about 3\,au-wide and made of small dust grains that lies under the coronagraph of the scattered-light image. Additionally, the weak central emission at 1.3\,mm could be part of this ring.
\end{enumerate}

Finally, we encourage additional detailed analysis and more modelling that could give some explanations of the substructures present on the disc. Higher resolution observations of radio continuum may provide the opportunity to make better measurements of the rings radial extension. For future radiative transfer models, it might be worth adding gas, using different inclinations for the inner and outer disc and implementing hydrodynamic simulations too, especially to try to unravel the mystery of how the inner ring is so thin an stable.

>>>>

Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig. \ref{fig:two}). Since this faint central emission is offset from the star, at the origin of coordinates in the figure, it is probably due to large dust grains. This dust structure is at a distance of only $\sim0\farcs02$ from the binary system, and may match the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.\,\ref{sec:***} below). If so, then given that the binary phase at the time of the observations is PA=***, so that the secondary lies roughly northwards of the primary, it may be that the northern side of Ring6 is shadowed, resulting in a seemingly lopsided geometry.

@@

The binary phase reported by \citet{dOrazi}  in the scattered-light observation is at a position angle (PA) of 360-106\,$\degr$, east of north. Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of 360-13\,$\degr$. There is no hint of  radio decrements  in  either Rings13 nor  in Ring24 that would match shadowing at this PA,   could be explained by inefficient disk cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.

@@

The multi-frequency data can be interpreted in terms of a physical
structure using radiative transfer predictions, for which we used the
\textsc{radmc3d} package\citep{Dullemond_2012}. The general framework
of the parametric model that we used is similar to that in
\citet{2018MNRAS.477.5104C} for DoAr\,44, and the initial model
values were inspired from those in \citet{Rosenfeld_2013}.

For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of log$\,\dot{\mathrm{M}} = -$9.3\,Myr$^{-1}$ for both cases \citep{10.1111/j.1365-2966.2011.19366.x}. The stars were placed at a  mutual separation of 0.041\,au, so that their center of mass coincides with the origin,  and oriented at a PA of *****  30\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by d'Orazzi****  rotation, relative to the semi-major axis of the disk, to match the shadows reported by \citet{dOrazi} **** GIVE ORIENTATION IN TERMS OF THE PA****

Reproducing  the  radial and vertical structure of the V4046\,Sgr disc turned out to be challenging.  We  built the model in terms of the gas distribution, and with  two different dust populations: larger grains that are vertically settled and dominate the total dust mass and a  population of smaller grains that are uniformly mixed with the gas and reach larger heights above the mid-plane.

Assuming a three dimensional model in a spherical reference frame with coordinates ($r$, $\theta$, $z$), the gas density ($\rho_{\mathrm{gas}}$) distribution follows
\begin{equation}
  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma(r) \,\delta(r)}{\sqrt{2\pi} \,r H(r)}  \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{r H(r)}\right)^2\right],
\end{equation}
where $\delta(r)$  parameterises the density drops in the gaps and cavities, $H(r)$ is the scale height profile and $\Sigma(r)$ is the surface density profile. $\Sigma(r)$ is defined by
\begin{equation}
  \Sigma(r) = \Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
\end{equation}
where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient. A fixed $\gamma$ = 1 is used as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.

The parametric scale height profiles for the gas and for each dust population are 
\begin{equation}
    \label{scale}
  H(r)=\chi \, H_{o}(r) \, [r/r_{o}(r)]^{\psi(r)},
\end{equation}
where $H_\circ$ is the scale height at r = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling. For the gas and the small dust grains $\chi$ = 1 and for the millimetre-size dust population we assign a fixed $\chi$ = 1/2 for simplicity, as in \citet{Rosenfeld_2013}.

For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one. ***explicar que es varphi y como se transforma en psi**** Our model uses the same values, with two   different flaring indeces $\psi$. The separation between the two values was set at $r$ = 19\,au with $\psi=0.2$ for  Ring6 and Ring13, and $\psi=0.5$ for Ring24. The scale height is  $H_\circ = 0.045$ at $r_0 = 19.5$\,au.

The small-dust density distribution follows the same behaviour as the gas, with a dust-to-gas mass ratio $\zeta = 0.047$ \citep[as in][]{Rosenfeld_2013}, the mass fraction between small and large dust particles $f_\mathrm{sd}=***$ and another factor for fine tuning that depends on the radius,  $\delta_{\mathrm{sd}}(r)$. The small dust density is thus given by 
\begin{equation}
\rho_{\mathrm{small-dust}}(r,z)=\rho_{\mathrm{gas}}(r,z)\, f_{\mathrm{sd}} \, \delta_{\mathrm{sd}}(r) \: \zeta .
\end{equation}
***I changed $f_{\mathrm{sd}}$  to $f_{\mathrm{sd}}$. say how much is $f_{sd}$.

Since the large-dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity and   scaling factors that account for  the larger gap between the rings. For the inner ring, the same profile as the gas is used, but with different values for $R_c$ and $\Sigma_c$. The greatest difference is in the outer ring, where we used a decaying power law modulated by the sum of two    Gaussian profiles. In an effort to recreate the break seen in the outer ring between 32 and 34.5\,au, we chose a different value for $\gamma$ = -8. For the large dust grains the surface density profile is thus
\begin{multline}
  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma}  \\ \, \left\{ \exp\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] +  \mathrm{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2}\right]\right\}.
\end{multline}

***REWORD PARA, IT IS NOT CLEAR WHERE DOES THIS EPSILON ENTERS - IF IT IS COMMON TO BOTH SPECIES, THEN INCLUDE IT IN THE GAS PROFILE. I DID NOT CHECK REDACTION, MAKE THIS AS COMPACT AS POSSIBLE***  Also for both dust populations, the inner part of the outer ring follows a different behaviour. The surface density profile is multiplied by an additional factor
\begin{equation}
    \epsilon(r) = \delta +  (1 - \delta) \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3,
\end{equation}
where $\delta=10^{-4}$ and $R_\mathrm{in}$ and $R_\mathrm{peak}$ would depend on the dust population, marking the beginning and the maximum density peak of the outer ring. This parameter allow us to model a smoother inner wall of the outer ring.

The two different populations of dust grains corresponds to  the small grains, with  radii ranging  from 0.4 to 1.5\,$\micron$, and the large dust grains range, with radii  from 0.4\,$\micron$ to 10\,mm. We computed the dust opacities using the {\tt bhmie} code, with  a mix composed of  70\% silicate and 30\% graphite.

The observed near-far asymmetry in the DPI image is suggestive of a strongly forward-scattering phase function. In order to reproduce a similar  asymmetry, we required much larger grains that typically used in the RT modeling of  such near-IR data \citep[e.g.][]{2018MNRAS.477.5104C}.

The simulated DPI image at 1.65\,$\micron$ in Fig.\,\ref{fig:two} was
obtained with the scattering matrix calculated by the {\tt makeopac.py}
script provided in the RADMC3D package. We used a  Gaussian size distribution centred at 0.4\,$\micron$, and smeared  out by 30\% in both directions, and using 20 grain size bins within  that range.

\begin{figure}
	\includegraphics[width=\columnwidth]{allprofiles.png}
        \caption{{\bf Top:}  surface density profiles for the gas, the large and small grain populations. {\bf Bottom:}  scale height profile $h(r)$. The dashed lines crossing both panels correspond to transition  radii in the parametric model.}
    \label{fig:profiles}
\end{figure}

Through trial and error, we found a set of values for the parameters that  correctly fit the available data. The final structure of the parametric model goes as Fig. \ref{fig:profiles} shows. The inner radius of the model grid was set to 0.1\,au and an outter radius of 115\,au, large enough for the dust disc to become undetectable.

The gas and small dust surface density profiles  begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$****. For the small dust grains, we propose a three ringed structure. The innermost ring of the model is located from 5 to 8\,au, this ring, introduced as Ring6 in Sec.\,\ref{sec:Observations}, is not detectable in the IRDIS  observations but was required to account for the  SED. Then follow the two  rings observed by IRDIS:  Ring13, from 12 to 19.5\,au, which is surrounded by very narrow  1\,au-wide gap, and then Ring24, that starts  20.5\,au and has its maximum density peak at 25\,au. The small-dust density  then decays exponentially with  radius.

On the other hand, in order to reproduce the double-ringed  morphology of the millimetre continuum emission,  we required a model with   a wide central cavity ($r = 12.3$\,au), a narrow 2.6\,au-wide inner ring (which is Ring13) followed by a 8.2\,au gap  that separates the  outer ring (Ring24), which starts at  23\,au and reaches peak  densities  at 27.3\,au. This last ring has an observed break between 32 and 34.5\,au, which is reproduced in the model with the a discontinuity in the exponent $\gamma$, along with the sum of the decaying exponentials. We also truncated  the model large-grain density at  $\sim$57\,au.

@@

The simulated 1.3\,mm continuum image  reproduces the two observed rings: the faint Ring13 and the  brighter Ring24. As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig. \ref{fig:radprofiles}), we can assume that the model provides an approximation of the disc structure, including the dimensions of  Ring13. Accordingly, taking the parametric model values for Ring13 we have that it has a radius of  13.6\,au,  a  width of 2.6\,au, and a  scale height ranging from 0.25 to 0.32\,au. The total dust mass of Ring13 is  about 3\,M$_{\earth}$ in the model.  In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then  breaks  at $\sim$35\,au, as in the observations, and has a total dust  mass of $\sim$43\,M$_{\earth}$.

****DISCUTIR EL ANCHO OBSERVADO VS. ANCHO MODELO****

As \citet{2018ApJ...869L..46D} explains, the stability of a narrow dust ring requires that its  height be smaller than its  radial extent ***HOW MUCH SMALLER?***. Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of Ring13 (4.17\,au FWHM, see Section \ref{sec:Observations}), we have that its width is $\sim$15 times its scale height.

***CHECK THAT THE RT PREDICTIONS USE THE SAME BEAM FOR CONVOLUTION AS THE DATA, AND UPDATE ALL FIGURES****

The observed SED was collected from data  in \citet{Jensen_97}, in \textsc{vizier} ***FOR WHICH BANDS?***  and \textsc{diana} ***idem***, and also using spectrometry data from an archival \textit{Spitzer} IRS spectrum.   ***THIS SHOULD GO IN SEC. OBS****

The observed SED is compared with the model in Fig. \ref{fig:SED}. From the similarity with the data we propose that there has to be a small-grain population close to the stars down to 0.3\,au. The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit ***WHERE in LBDA?****, and we may have detected this ring in the ALMA image, if this ring is  lopsided or shadowed by the secondary.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{SED_.png}
    \caption{The observed SED of V4046\,Sgr  (black points and solid red curve) compared with the model (blue). The black points represent the measured photometry and the red line shows an archival \textit{Spitzer} IRS spectrum. The dashed silver curve shows the emission of the stellar photosphere model.}
    \label{fig:SED}
\end{figure}

@@

New ALMA 1.3\,mm continuum imaging of the circumbinary disc around V4046\,Sgr were analysed in the context of the available IR imaging and the observed spectral energy distribution using a RT model.  The key conclusions are as follows.
\begin{enumerate}

\item We report the detection of a narrow ring in the 1.3\,mm continuum, with a  radius 13.46$\pm$0.43\,au and an estimated width of 4.17$\pm$0.94\,au **UPDATE FOR NEW BEAM***. The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 3\,M$_{\earth}$ millimetre-sized grains. Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is $\sim$15 times its estimated height ***UPDATE****

  \item The 1.3\,mm outer ring, that starts at $\sim$23\,au and has its peak intensity at $\sim$32\,au, presents a visible break in the surface brightness at $\sim$35\,au. 
  \item We interpret the asymmetry observed with SPHERE-IRDIS at 1.65\,$\micron$ as due to strong forward-scattering, which implies that the dust population is depleted of grains smaller than $\sim$0.4\,$\micron$.

  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars ***IS THIS NOT A CONFIRMATION OF THE INNER DIST PROPOSED BY ROSENFELD+? IF SO, SAY SO****. We also predict the existence of another thin ring at $\sim$6\,au, about 3\,au-wide and made of small dust grains, and  that lies under the coronagraph of the scattered-light image. The weak central emission at 1.3\,mm could be part of this ring.
\end{enumerate}
